Climate control for performant HPUs

### 2014-04-09 docs/draft/draft1.tex
update to manuscript

>>>>

We paid 900 AMT workers to perform an image-labelling task.  Each worker
was randomly assigned to one of 6 priming treatments. A task consisted of 
labelling 10 images, with 5 labels each.  The first 5 images were varied 
depending on the priming treatment, and this was used to explore the effects
of \textit{in-task} priming.  The last 5 images were the same accross all 
treatments, and served as the primary means of assessing the effects of 
the priming treatments.

The test images were chosen with two ideals in mind.  First, we chose images
that we felt would generate a diverse vocabulary of labels, such that the
effects of priming could be detected.  Images that are sparse, and with a 
very strong foreground might produce a narrow distribution of labels that 
would not exhibit the effects of priming as much.

Second, we chose images which would produce labels belonging to two broad
concepts, food and culture.  The purpose of this was to test to what
extent workers could be biased in favor of focusing on one concept or the other
during labelling.

We divide our treatments into three broad classes: \textit{ambiguous}, 
\textit{culture}, and \textit{food}.
\section*{Results}
\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity.pdf}
\end{figure*}
